Estimation of cloud-corrected microwave humidity radiances with associated uncertainties

### 2020-11-13 Article/ici_submm_cloudcorr.tex
changes in Fig12, more details in AWS results

A methodology based on quantile regression neural networks (QRNN) is presented that identifies and corrects the cloud impact on microwave humidity sounder radiances at 183GHz. This approach estimates the posterior distributions of noise free clear-sky (NFCS) radiances, providing nearly bias-free estimates of clear-sky radiances with a full posterior error distribution. It is first demonstrated by application to a present sensor, the MicroWave Humidity Sounder-2 (MWHS-2), then the applicability to sub-millimeter (sub-mm) sensors is also analysed. The QRNN results improve upon what operational cloud filtering techniques like a scattering index can achieve, but are ultimately imperfect due to limited information content on cirrus impact from traditional microwave channels---the negative departures associated with high cloud impact are successfully corrected, but thin cirrus clouds cannot be fully corrected. In contrast, when sub-mm observations are used, QRNN successfully corrects most cases with cloud impact, with only 2-6\% of cases left partially corrected. The methodology works well even if only one sub-mm channel (325\,GHz) is available. When using sub-mm observations, cloud correction usually results in error distributions with standard deviation less than typical channel noise values. Furthermore, QRNN outputs predicted quantiles for case-specific uncertainty estimates, successfully representing the uncertainty of cloud correction for each observation individually. In comparison to deterministic correction or filtering approaches, the corrected radiances and attendant uncertainty estimates have great potential to be used efficiently in assimilation systems due to being largely unbiased and adding little further uncertainty to the measurements.

@@

\subsection{Quantile regression neural networks}
\label{sec:QRNN}
%
The task that we aim to solve in this study is to predict the NFCS brightness
temperature \todo{$\ynfcs$} at a given $183\unit{GHz}$ channel from a vector of
all-sky observations $\y$. Since the information-content of the
cloud-contaminated observations is certainly too low to solve this problem
exactly, a probabilistic formulation is appropriate here. The aim thus becomes
to predict the conditional distribution $p(\ynfcs | \y)$ of the NFCS brightness
temperatures $\ynfcs$ given the cloud-contaminated observations $\y$.

@@

All evaluation results except hyper-parameter tuning, described in the study, have been made on the test dataset. Hyper-parameter tuning is made on the validation dataset (see Appendix~\ref{appendix:hyperparamter}). Validation dataset is part of the training dataset which is held back during the training process.

\section{Correcting cloud affected data in MWHS-2}
\label{qrnn_mwhs}
%
In this section, we introduce the QRNN based cloud correction in the context of current operational sensors.  We use MWHS-2 to demonstrate the results. The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels, along with additional 118\,GHz channels. In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2. However, for brevity we compare the comprehensive results only for channel 14. Later the optimal experiment is extended to other 183\,GHz channels. A brief comparison of the results is also made against existing cloud filtering methods. Further, the estimates of case-specific uncertainties obtained from QRNN are also evaluated.

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/QRNN_output_mwhs.pdf} 
	\caption{The distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/MWHS_error_dist_14.pdf} 
	\caption{The error distribution for deviations of point estimates to NFCS simulations. The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14. Noise is also plotted for reference. The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates. The error distribution achieved with scattering index (SI) filtering is also shown. }
	\label{fig:error_distribution_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{The error statistics for deviations of point estimates to NFCS simulations. Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}). The statistics for all-sky and clear-sky simulations are also provided. The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded. The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183). Bias, MAE, STD are in K, skewness in dimensionless.}
	\label{tab:error_statistics_mwhs_14}
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
		\cline{2-13}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)&&\\
		\middlehline
Bias     & -0.00 &  -0.83 & -0.09 & -0.08 & -0.04 & -0.03 & -0.09 & -0.09 & -0.09 & -0.08 & -0.24 & -0.51\\
MAE      &  0.80 &   1.44 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59 &  0.92 &  1.14\\
STD      &  1.00 &   3.89 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83 &  1.26 &  1.83\\
Skewness &  0.01 & -14.40 & -1.11 & -0.96 & -1.02 & -0.86 & -0.89 & -1.02 & -1.61 & -1.58 & -1.79 & -3.45\\
Rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.1\%& 3.5\%\\
\bottomhline
	\end{tabular}
\end{table*}

The posterior distribution of $\ynfcs$ obtained from experiment 89+150\,GHz is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V}. The median value is chosen as the point estimate (see Sect.~\ref{sec:validation}). The distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}. The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed. However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently. The deviations of point estimates to NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}. The large negative deviations are corrected successfully with QRNN (blue curve), but residual cloud impact is evident in the negative tail. Most of these residual cases have departures less than 10\,K. The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness(-14.34) and high bias (-0.84\,K). QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.09\,K. However, high skewness values indicate a negative tail or uncorrected departures. Including 118\,GHz in the training gives comparable results as 89+150\,GHz. With 118\,GHz, the error distribution has lower bias and are more symmetric, but the MAE and STD remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz. In the latter, predictions have the most symmetric error distributions, but the highest spread.

@@

In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}. SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases. They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ and $183.31\pm 1.00$ as a measure of cloud impact. Further in the text we refer this filter as ``B183''. The results obtained with SI and B183 are displayed in last two columns of Table~\ref{tab:error_statistics_mwhs_14}. With SI threshold = 5\,K, almost 28\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN. The low bias and skewness values indicate that most of the high negative departures are removed, but cases with low cloud impact pass the filter as clear. Similar is the case with B183. Here only 3\% of the data is filtered out but the overall statistics are worse than both QRNN and SI. The results from the two filters are not surprising as both aim at removing only cases with high ice content. The thin cirrus clouds and other low hydrometeor impact cases remain unaltered.

@@

\subsubsection{Comparison of QRNN-all and QRNN-single}
%
%f
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/correlation.pdf} 
	\caption{ The triangular error correlation matrix obtained from QRNN-single and QRNN-all for MWHS-2. The label ``Clear'' represents cases with cloud impact less than 2\,K.}
	\label{fig:correlations_mwhs}	
\end{figure}
To assess the differences between the capabilities of QRNN-all against QRNN-single, we  compare the error statistics obtained for 89+150\,GHz and 89+150+183\,GHz for channel 14.  Table~\ref{tab:error_statistics_mwhs_14} shows the error statistics for the experiment QRNN-all. In comparison to QRNN-single, we obtain marginally lower error bias with QRNN-all, and the MAE and standard deviation reduce by almost 30\% and 25\% respectively. However, the negative tail becomes more prominent. The low standard deviation, but strong negative tail indicates that the narrow spread is a consequence of correction of noise in clear-sky cases. Since a majority of the cases are clear-sky, their impact dominates the whole statistics. In order to probe the positive effect of QRNN-all, we also estimate the errors for all cases with cloud correction greater than 5\,K. In comparison with QRNN-single, QRNN-all has slightly better accuracy. This suggests that concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.

Even though QRNN-all gives slightly better prediction accuracy, its inherent construction makes it crucial to examine the correlation between observed errors. Fig.~\ref{fig:correlations_mwhs} illustrates the correlation matrix for both QRNN-all and QRNN-single. For clear cases, the observed errors (noise) in QRNN-single are uncorrelated between the five channels. However QRNN-all gives out highly correlated errors. The correlations are highest between adjacent channels, and drop out as the spacing between the channels increases. For cloudy cases, the observed errors obtained from QRNN-single are slightly correlated, but with QRNN-all a very strong correlation is observed (not shown).

\subsubsection{QRNN-single applied to channel 11, 12, 13 and 15}
\label{sec:mwhs_others}
\begin{table*}[t]
	\caption{ Error statistics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz. The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}. The statistics from existing filtering approaches: scattering index (SI), and scheme by \citet{buehler:aclou:07} (B183) are also provided.}
	\label{tab:error_statistics_mwhs_others}
	\begin{tabular}{lrrr|rr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c|}{QRNN-single} & \multicolumn{2}{c}{Pure filtering} \\
		\cline{2-8}
		%		\hline
		& &  Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz}    & SI & B183  \\
		&	&		   &			& All & Pred.(5\,K) &&\\
		\middlehline
		Channel 11  &   Bias      & 0.00 &  -0.16 & -0.03 & -0.03		 &-0.04	& -0.05 \\
				    &	MAE       & 0.80 &   0.89 &  0.79 &  0.79  		 & 0.81	&  0.81 \\
					&	STD       & 1.00 &   1.71 &  1.03 &  1.01 		 & 1.02	&  1.03 \\
					&	Skewness  & 0.01 & -20.18 & -0.68 & -0.45 		 &-0.12 & -0.24 \\
					& Rejection   & -    & -      & -	  & 0.2\%        & 28.1\% & 3.5\%  \\
		\middlehline
		Channel 12  & Bias      & -0.00 &  -0.28 & -0.05 & -0.05		&  -0.07 & -0.15 \\
					& MAE       &  0.80 &   0.98 &  0.81 &  0.80  		&   0.82 &	0.86 \\
					& STD       &  1.00 &   2.26 &  1.07 &  1.05  		&  1.04  &  1.14 \\
					& Skewness  &  0.00 & -20.72 & -0.91 & -0.70  		&  -0.38 & -0.86 \\
					& Rejection & -    & -      & -	  & 0.6\%        & 28.1\% & 3.5\%  \\
		\middlehline
		Channel 13  & Bias      & -0.00 &  -0.52 & -0.08 & -0.07 		& -0.14  & -0.29 \\
					& MAE       &  0.80 &   1.17 &  0.84 &  0.83  		&  0.86  &  0.97 \\
					& STD       &  1.00 &   3.04 &  1.13 &  1.10  		&  112  &	1.39 \\
					& Skewness  &  0.02 & -17.85 & -1.14 & -0.98  		& -0.91  & -2.23 \\	
					& Rejection   & -    & -      & -	  & 1.6\%        & 28.1\% & 3.5\%  \\	
		\middlehline
		Channel 15  & Bias      & -0.00 &  -1.28 & -0.07 & -0.06        & -0.33 &  -0.81 \\
					& MAE       &  0.80 &   1.87 &  0.97 &  0.92 		&  1.03 &	1.44 \\
					& STD       &  1.00 &   5.08 &  1.35 &  1.25 		&  1.53 &	2.64 \\
					& Skewness  & -0.00 & -11.15 & -0.60 & -0.83 		& -2.85 &  -4.41 \\ 
					& Rejection & -     & -      & -	 & 5.6\%        & 28.1\% & 3.5\%  \\
		\bottomhline
	\end{tabular}
\end{table*}

@@

For channel 11, the error bias after correction is only -0.03\,K in comparison to 0.16\,K before correction. The strong negative tail also diminishes after correction, but a non-zero negative skewness indicates presence of cases with residual cloud impact in the corrected dataset. Filtering the cases with high cloud impact has only a marginal positive effect. A similar performance is evident for channel 12. Correction reduces the bias to -0.05\,K and standard deviation to 1.07\,K. The MAE is approximately 17\% lower after correction, but still the negative skewness is not removed completely. For channel 13 and 15 also, a similar performance is seen. But in the latter, error distributions are most symmetric but with largest spread as compared to other four channels.

A comparison with SI based filtering and B183 is displayed in last columns of Table~\ref{tab:error_statistics_mwhs_others}. For channel 11 the performance of QRNN is comparable to both SI and B183. Similar is the case with channel 12, though the results from B183 are slightly poorer. Both these channels are mostly transparent to hydrometeor impact, and the filtering schemes work well. The major caveat is the rejection of clear cases. With comparable accuracy, the fraction of rejection in SI is approx. 28\% in comparison to approx. 3\% in B183. For channels 13 and 15 the error statistics obtained with SI are slightly inferior in comparison to QRNN. The results with B183 are even worse. For all channels, the two filters succeed in removing the high ice cloud cases, but for lower peaking channels, the high negative skewness values indicate presence of cases with low cloud impact. Clearly the ``one for all'' approach of both filters is not adequate to cater for channel specific hydrometeor impact.

@@

The quantiles given out by QRNN can be used to construct the probability distribution of the predictions in contrast to other correction approaches which give out only point estimates. Examples of the uncertainties given out by QRNN are shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}. The spread of error distribution is asymmetric. The predictions over quantiles $-3\sigma$, $-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value. In contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and $3\sigma$ is wider. Also, cases with very high uncertainty occur infrequently. The box plots show that all the quantiles, except $3\sigma$ also follow the Gaussian distribution.

The calibration of the prediction intervals is displayed in Fig.~\ref{fig:calibration_mwhs}. For the entire dataset, the predictions follow the $y=x$ line, i.e. the predicted uncertainties are perfectly calibrated with the errors observed on the test data. However for the cases with correction greater than 5\,K, the distribution is poorly calibrated, and the curve lies below the $y =x$ line, indicating that the prediction intervals are too narrow. This is in agreement with the wider spread of predictions over the  higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}). However such cases form less than 6\% of the dataset and filtering them has little effect on the overall calibration.

@@

	\item In the second experiment, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz. This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available. In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel. For example, for target AWS-32, the training inputs are AWS-32, AWS-41, AWS-42, AWS-43, AWS-44. QRNN is trained five times for each 183\,GHz channel as target. Note that for this experiment, AWS was chosen due to availability of extra 325\,GHz and 183\,GHz channels. 	
\end{enumerate}

>>>>

A methodology based on quantile regression neural networks (QRNN) is presented that identifies and corrects the cloud impact on microwave humidity sounder radiances at 183\,GHz. This approach estimates the posterior distributions of noise free clear-sky (NFCS) radiances, providing nearly bias-free estimates of clear-sky radiances with a full posterior error distribution. It is first demonstrated by application to a present sensor, the MicroWave Humidity Sounder-2 (MWHS-2), then the applicability to sub-millimeter (sub-mm) sensors is also analysed. The QRNN results improve upon what operational cloud filtering techniques like a scattering index can achieve, but are ultimately imperfect due to limited information content on cirrus impact from traditional microwave channels---the negative departures associated with high cloud impact are successfully corrected, but thin cirrus clouds cannot be fully corrected. In contrast, when sub-mm observations are used, QRNN successfully corrects most cases with cloud impact, with only 2-6\% of cases left partially corrected. The methodology works well even if only one sub-mm channel (325\,GHz) is available. When using sub-mm observations, cloud correction usually results in error distributions with standard deviation less than typical channel noise values. Furthermore, QRNN outputs predicted quantiles for case-specific uncertainty estimates, successfully representing the uncertainty of cloud correction for each observation individually. In comparison to deterministic correction or filtering approaches, the corrected radiances and attendant uncertainty estimates have great potential to be used efficiently in assimilation systems due to being largely unbiased and adding little further uncertainty to the measurements.

@@

\subsection{Quantile regression neural networks}
\label{sec:QRNN}
%
The task that we aim to solve in this study is to predict the NFCS brightness
temperature \todo{$\ynfcs$} at a given 183\,GHz channel from a vector of
all-sky observations $\y$. Since the information-content of the
cloud-contaminated observations is certainly too low to solve this problem
exactly, a probabilistic formulation is appropriate here. The aim thus becomes
to predict the conditional distribution $p(\ynfcs | \y)$ of the NFCS brightness
temperatures $\ynfcs$ given the cloud-contaminated observations $\y$.

@@

All evaluation results except hyper-parameter tuning, described in the study, have been made on the test dataset. The hyper-parameter tuning is made on the validation dataset (see Appendix~\ref{appendix:hyperparamter}). The validation dataset is part of the training dataset which is held back during the training process.

\section{Correcting cloud affected data in MWHS-2}
\label{qrnn_mwhs}
%
In this section, we introduce the QRNN based cloud correction in the context of current operational sensors.  We use MWHS-2 to demonstrate the results. The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels, along with additional 118\,GHz channels. In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2. However, for brevity we show the comparison of the comprehensive results only for channel 14. Later the optimal experiment is extended to other 183\,GHz channels. A brief comparison of the results is also made against existing cloud filtering methods. Further, the estimates of case-specific uncertainties obtained from QRNN are also evaluated.

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/QRNN_output_mwhs.pdf} 
	\caption{The distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/MWHS_error_dist_14.pdf} 
	\caption{The error distribution for deviations of point estimates to NFCS simulations. The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14. Noise is also plotted for reference. The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates. The error distribution achieved with scattering index (SI) filtering is also shown. }
	\label{fig:error_distribution_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{The error statistics for deviations of point estimates to NFCS simulations. Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}). The statistics for all-sky and clear-sky simulations are also provided. The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded. The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183). Bias, MAE, STD are in K, skewness is dimensionless.}
	\label{tab:error_statistics_mwhs_14}
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
		\cline{2-13}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)&&\\
		\middlehline
Bias     &  0.00 &  -0.84 & -0.10 & -0.09 & -0.05 & -0.04 & -0.11 & -0.10 & -0.10 & -0.09 & 0.24  & -0.52\\
MAE      &  0.80 &   1.45 &  0.89 &  0.87 &  0.90 &  0.88 &  0.90 &  0.88 &  0.62 &  0.60 & 0.92  & 1.15\\
STD      &  1.00 &   3.73 &  1.20 &  1.16 &  1.21 &  1.16 &  1.22 &  1.18 &  0.91 &  0.85 & 1.26  & 1.86\\
Skewness & -0.02 & -12.72 & -1.17 & -1.00 & -1.06 & -0.90 & -1.16 & -1.04 & -1.78 & -1.71 &-1.95  & -3.45\\
Rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.8\%& 3.5\%\\
\bottomhline
	\end{tabular}
\end{table*}

The posterior distribution of $\ynfcs$ obtained from experiment 89+150\,GHz is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V}. The median value is chosen as the point estimate (see Sect.~\ref{sec:validation}). The distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}. The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed. However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently. The deviations of point estimates to NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}. The large negative deviations are corrected successfully with QRNN (blue curve), but residual cloud impact is evident in the negative tail. Most of these residual cases have departures less than 10\,K. The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness(-12.72) and high bias (-0.84\,K). QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.10\,K. However, high skewness values indicate a negative tail or uncorrected departures. Including 118\,GHz in the training gives comparable results as 89+150\,GHz. With 118\,GHz, the error distribution has lower bias and are more symmetric, but the MAE and STD remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz.

@@

In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}. SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases. They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ \,GHz and $183.31\pm 1.00$ \,GHz as a measure of cloud impact. Further in the text we refer this filter as ``B183''. The results obtained with SI and B183 are displayed in last two columns of Table~\ref{tab:error_statistics_mwhs_14}. With SI threshold = 5\,K, almost 28\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN. The low bias and skewness values indicate that most of the high negative departures are removed, but cases with low cloud impact pass the filter as clear. Similar is the case with B183. Here only 3\% of the data is filtered out but the overall statistics are worse than both QRNN and SI. The results from the two filters are not surprising as both aim at removing only cases with high ice content. The thin cirrus clouds and other low hydrometeor impact cases remain unaltered.

@@

\subsubsection{Comparison of QRNN-all and QRNN-single}
%
%f
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/correlation.pdf} 
	\caption{ The triangular error correlation matrix obtained from QRNN-single and QRNN-all for MWHS-2. The label ``Clear'' represents cases with cloud impact less than 2\,K.}
	\label{fig:correlations_mwhs}	
\end{figure}
To assess the differences between the capabilities of QRNN-all against QRNN-single, we  compare the error statistics obtained for 89+150\,GHz and 89+150+183\,GHz for channel 14.  Table~\ref{tab:error_statistics_mwhs_14} shows the error statistics for the experiment QRNN-all. In comparison to QRNN-single, we obtain almost similar error bias with QRNN-all, but the MAE and standard deviation reduce by almost 30\% and 24\% respectively. However, the negative tail becomes more prominent. The low standard deviation, but strong negative tail indicates that the narrow spread is a consequence of correction of noise in clear-sky cases. Since a majority of the cases are clear-sky, their impact dominates the whole statistics. In order to probe the positive effect of QRNN-all, we also estimate the errors for all cases with cloud correction greater than 5\,K. In comparison with QRNN-single, QRNN-all has slightly better accuracy. This suggests that concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.

Even though QRNN-all gives slightly better prediction accuracy, its inherent construction makes it crucial to examine the correlation between observed errors. Figure~\ref{fig:correlations_mwhs} illustrates the correlation matrix for both QRNN-all and QRNN-single. For clear cases, the observed errors (noise) in QRNN-single are uncorrelated between the five channels. However QRNN-all gives out highly correlated errors. The correlations are highest between adjacent channels, and drop out as the spacing between the channels increases. For cloudy cases, the observed errors obtained from QRNN-single are slightly correlated, but with QRNN-all a very strong correlation is observed (not shown).

\subsubsection{QRNN-single applied to channel 11, 12, 13 and 15}
\label{sec:mwhs_others}
\begin{table*}[t]
	\caption{ Error statistics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz. The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}. The statistics from existing filtering approaches: scattering index (SI), and scheme by \citet{buehler:aclou:07} (B183) are also provided.}
	\label{tab:error_statistics_mwhs_others}
	\begin{tabular}{lrrr|rr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c|}{QRNN-single} & \multicolumn{2}{c}{Pure filtering} \\
		\cline{2-8}
		%		\hline
		& &  Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz}    & SI & B183  \\
		&	&		   &			& All & Pred.(5\,K) &&\\
		\middlehline
		Channel 11  & Bias     & -0.00 &  -0.15 & -0.12 & -0.12 & -0.04 & -0.05\\
					& MAE      &  0.80 &   0.88 &  0.80 &  0.80 &  0.81 & 0.81 \\
					& STD      &  1.00 &   1.51 &  1.03 &  1.02 &  1.02 & 1.03 \\
					& Skewness &  0.01 & -15.73 & -0.61 & -0.45 & -0.07 & -0.29\\
					& Rejection   & -    & -      & -	  & 0.2\% & 28.8\% & 3.5\%  \\
		\middlehline
		Channel 12  &  Bias     & -0.01 &  -0.29 & -0.12 & -0.11  & -0.08 & -0.16\\
					&  MAE      &  0.80 &   0.98 &  0.82 &  0.81  &  0.82 & 0.87\\
					&  STD      &  1.00 &   2.02 &  1.08 &  1.06  &  1.04 & 1.15\\
					&  Skewness & -0.01 & -17.27 & -0.96 & -0.79  &  -0.25 & -1.02 \\
					& Rejection & -     & -      & -	 & 0.6\%  & 28.8\% & 3.5\%  \\
		\middlehline
		Channel 13  &Bias       & 0.00 &  -0.53 & -0.11 & -0.10 & -0.14 & -0.31\\
					&MAE        & 0.80 &   1.18 &  0.85 &  0.84 &  0.86 & 0.98\\
					&STD        & 1.00 &   2.83 &  1.15 &  1.12 &  1.12 & 1.41 \\
					&Skewness   & 0.01 & -15.24 & -1.22 & -1.08 & -1.03 & -2.30\\  	
					& Rejection & -     & -      & -	 & 1.6\%& 28.8\% & 3.5\%  \\	
		\middlehline
		Channel 15  &  Bias     & 0.00 &  -1.28 & -0.09 & -0.07 & -0.33 & -0.83\\
					&  MAE      & 0.80 &   1.88 &  0.98 &  0.93 &  1.03 &  1.46\\
					&  STD      & 1.00 &   4.97 &  1.36 &  1.27 &  1.52 &  2.69\\
					&  Skewness & 0.00 & -10.11 & -0.69 & -0.82 & -2.87 &  -4.33 \\ 
					& Rejection & -     & -      & -	 & 5.5\% & 28.8\%& 3.5\%  \\
		\bottomhline
	\end{tabular}
\end{table*}

@@

For channel 11, the error bias after correction is  -0.12\,K in comparison to 0.15\,K before correction. The strong negative tail also diminishes after correction, but a non-zero negative skewness indicates presence of cases with residual cloud impact in the corrected dataset. Filtering the cases with high cloud impact has only a marginal positive effect. A similar performance is evident for channel 12. Correction reduces the bias to -0.12\,K and standard deviation to 1.08\,K. The MAE is approximately 16\% lower after correction, but still the negative skewness is not removed completely. For channel 13 and 15 also, a similar performance is seen. But in the latter, error distributions are most skewed and have a larger spread as compared to other four channels. The impact of poor predictions is highest in channel 15 owing to its sensitivity to hydrometeor impact.

A comparison with SI based filtering and B183 is displayed in last columns of Table~\ref{tab:error_statistics_mwhs_others}. For channel 11 the performance of QRNN is comparable to both SI and B183. Similar is the case with channel 12 and channel 13, though the results from B183 are slightly poorer. The higher peaking channels are mostly transparent to hydrometeor impact, and the filtering schemes work well. The major caveat is the rejection of clear cases. With comparable accuracy, the fraction of rejection in SI is approx. 28\% in comparison to approx. 3\% in B183. For channel, 15 the error statistics obtained with SI are slightly inferior in comparison to QRNN. The results with B183 are even worse. For all channels, the two filters succeed in removing the high ice cloud cases, but for lower peaking channels, the high negative skewness values indicate presence of cases with low cloud impact. Clearly the ``one for all'' approach of both filters is not adequate to cater for channel specific hydrometeor impact.

@@

The quantiles given out by QRNN can be used to construct the probability distribution of the predictions in contrast to other correction approaches which give out only point estimates. Examples of the uncertainties given out by QRNN are shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}. The spread of error distribution is asymmetric. The predictions over quantiles $-3\sigma$, $-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value. In contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and $3\sigma$ is wider. The box plots indicate that cases with very high uncertainty occur infrequently. Also, all quantiles but  $3\sigma$, follow the Gaussian distribution.

The calibration of the prediction intervals is displayed in Fig.~\ref{fig:calibration_mwhs}. For the entire dataset, the predictions follow the $y=x$ line, i.e. the predicted uncertainties are perfectly calibrated with the errors observed on the test data. However for the cases with correction greater than 5\,K, the distribution is poorly calibrated, and the curve lies below the $y =x$ line, indicating that the prediction intervals are too narrow. This is in agreement with the wider spread of uncertainties for cases with low accuracy (Fig.~\ref{fig:prediction_uncertainty_mwhs}). However such cases form less than 6\% of the dataset and filtering them has little effect on the overall calibration.

@@

	\item In the second experiment, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz. This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available. In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel. For example, for the target AWS-32, the training inputs are AWS-32, AWS-41, AWS-42, AWS-43, AWS-44. QRNN is trained five times for each 183\,GHz channel as target. Note that for this experiment, AWS was chosen due to availability of extra 325\,GHz and 183\,GHz channels. 	
\end{enumerate}
